Development of Performance Regression Analysis Tool using Distributed Tracing on microservice-based Application\\

### 2022-09-07 paper.tex
txs auto checkin

@@

\begin{table}[htb]
	\caption{Test Cases}
	\label{testcases}
%	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		Checkout/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		Checkout/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		Checkout/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		Checkout/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		Checkout/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		Checkout/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		Checkout/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

@@

%\pagebreak

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
%\pagebreak
%
\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.

>>>>

\begin{table}[htb]
	\caption{Test Cases}
	\label{testcases}
	%	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		Checkout/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		Checkout/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		Checkout/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		Checkout/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		Checkout/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		Checkout/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		Checkout/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to \\ 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to \\ 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

@@

@@

\pagebreak

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak
%
\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.
